%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{todonotes}
\usepackage[skins]{tcolorbox}

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Lena} % Your first name
\familyname{Collienne} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
% \address{123 Broadway}{City, State 12345}
% \mobile{(000) 111 1111}
% \phone{(000) 111 1112}
% \fax{(000) 111 1113}
% \email{lena@lenacoll.de}
% \homepage{lenacoll.de}{lenacoll.de} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
% \extrainfo{additional information}
% \photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
% \quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

% \clearpage

% \recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
% \date{\today} % Letter date
% \opening{Dear Sir or Madam,} % Opening greeting
% \closing{Sincerely yours,} % Closing phrase
% \enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

% \makelettertitle % Print letter title

% \lipsum[1-2] % Dummy text
% \lipsum[4] % Dummy text

% \makeletterclosing % Print letter signature

% \newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------
\makecvtitle % Print the CV title

\vspace{-2cm}
\tcbset{size=small, sharp corners, colframe=black!0!white, width=5.3cm,box align=top,nobeforeafter}
\begin{tcolorbox}
    Email: \href{mailto:lena@lenacoll.de}{lena@lenacoll.de}\\
    Homepage: \href{https://www.lenacoll.de}{lenacoll.de}\\
    GitHub: \href{https://github.com/lenacoll}{github.com/lenacoll}
\end{tcolorbox}
\vspace{1cm}

%----------------------------------------------------------------------------------------
%	MAJOR RESEARCH PROJECT
%----------------------------------------------------------------------------------------

\section{Research}

\todo[inline]{Maybe just one point about current research/general research, and then list the other ones in Education/Work experience (without any specifics?)}
\cventry{}{Postdoctoral Research}{University of Canterbury}{Statistical Methods for Phylogenetic Time Trees}{}{}

\cventry{}{PhD Research}{University of Otago}{Spaces of Phylogenetic Time Trees}{}{Introducing and analysing a space of phylogenetic time trees (evolutionary histories), focusing on discrete time trees.
This includes establishing an algorithm for computing shortest paths between trees in the resulting tree space and analysing its properties.}

\cventry{}{M.Sc. Research}{University of Greifswald}{The ranked Nearest Neighbour Interchange space of phylogenetic trees}{}{Establishing a tree space of ranked phylogenetic trees and investigating its properties.}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2018--2021}{Doctor of Philosophy}{Computer Science}{University of Otago (NZ)}{}{}  % Arguments not required can be left empty
\cventry{2016--2018}{Master of Science}{Biomathematics}{University of Greifswald (GER)}{}{}
\cventry{2012--2015}{Bachelor of Science}{Biomathematics}{University of Greifswald (GER)}{}{}{}

% \section{PhD Thesis}

% \cvitem{Title}{\emph{Spaces of Phylogenetic Time Trees}}
% \cvitem{Supervisors}{Associate Professor Alex Gavryushkin \& Professor David Bryant}
% \cvitem{Description}{}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Work Experience}


\cventry{2022}{Postdoctoral Research Fellow}{BioDS lab, School of Mathematics and Statistics}{University of Canterbury (NZ)}{}{}

%------------------------------------------------
\subsection{Teaching}
\cventry{2022}{Lecturer}{STAT211: Random Processes}{University of Canterbury (NZ)}{}{}
\cventry{2019}{Tutor}{COSC341: Theory of Computing}{University of Otago (NZ)}{}{}

\todo[inline]{How do I add this?}
\subsection{Other}
\cventry{2015--2016}{Summer Research Project}{University of Auckland (NZ)}{}{}{Computational complexity of space of phylogenetic time trees}




%------------------------------------------------
%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Scholarships and Awards}

\cvitem{2021}{\textit{Exceptional PhD thesis} (Division of Science, University of Otago)}
\cvitem{2021}{\textit{Best Student Talk} (Phylomania Conference 2021)}
\cvitem{2018--2021}{\textit{University of Otago Doctoral Scholarship}}
\cvitem{2018}{\textit{Externally Funded Research Grant} (Max Planck Institute Pl\"on)}
\cvitem{2015}{\textit{Summer Research Scholarship} (University of Auckland)}
\cvitem{2015}{\textit{PROMOS Scholarship} (University of Greifswald)}
\cvitem{2014--2015}{\textit{Deutschlandstipendium} (Alfried Krupp von Bohlen und Halbach Foundation/Federal Government of Germany)}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\todo[inline]{Do I need this section? + Are the details given there accurate?}
\section{Computer skills}

\cvitem{Basic}{\textsc{java}, \textsc{C++}, \textsc{Perl}}
\cvitem{Intermediate}{\textsc{C}, \textsc{R}, \textsc{Python}}
\cvitem{Advanced}{\LaTeX}

%----------------------------------------------------------------------------------------
%	Additional Activities
%----------------------------------------------------------------------------------------

\section{Additional Activities}

\cvitem{2021}{President of the Otago Computer Science Society (University of Otgao)}
\cvitem{2019--2021}{Member of the Postgraduate Committee (Department of Computer Science, University of Otago)}
\cvitem{2019--2021}{Organising the annual Postgraduate Symposium (Department of Computer Science, University of Otago)}
\cvitem{2019--2021}{Member of Student Council (Institute for Mathematics and Computer Science, University of Greifswald)}

%----------------------------------------------------------------------------------------
%	Talks
%----------------------------------------------------------------------------------------

\section{Talks}

\subsection{Conference}


\cvitem{2021}{\textit{Distances between phylogenetic time trees}, Phylomania}
\cvitem{2021}{\textit{The space of discrete coalescent trees}, New Zealand Phylogenomics Meeting}
\cvitem{2020}{\textit{Online Algorithms in Computational Biology}, New Zealand Phylogenomics Meeting}
\cvitem{2019}{\textit{The Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees}, New Zealand Phylogenomics Meeting}

\subsection{Invited Seminars}
\cvitem{2021}{\textit{The Space of Discrete Coalescent Trees} (Department of Mathematics, University of Otago)}
\cvitem{2020}{\textit{Computing the Ranked Nearest Neighbour Interchange distance between ranked phylogenetic trees}, Online Seminars on Algorithms and Complexity in Phylogenetics}
\cvitem{2019}{\textit{The Ranked Nearest Neighbour Interchange space of phylogenetic trees}, Max Planck Institute for Mathematics in the Science}
\cvitem{2017}{\textit{Discrete time trees}, Computational Evolution Group, ETH Zurich}


\subsection{Other}
\cvitem{2022}{\textit{How to give a (good) talk}, School of Mathematics and Statistics, University of Canterbury}
\cvitem{2020}{\textit{The complexity of computing the RNNI distance between phylogenetic trees}, Postgraduate Symposium, Computer Science, University of Otago}
\cvitem{2020}{\textit{The complexity of computing nearest neighbour interchange distances between ranked phylogenetic trees}, Seminar of Departments of Computer Science and Information Science, University of Otago}
\cvitem{2019}{\textit{Online Algorithms in Computational Biology}, Postgraduate Symposium, Department of Computer Science, University of Otago}
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------

\section{Publications}

\cvitem{}{Bouckaert, R., \textbf{Collienne, L.} \& Gavryushkin, A. (2022). Online Bayesian Analysis with BEAST2. \textit{BioRxiv}.}

\cvitem{}{\textbf{Collienne, L.} (2021). Spaces of phylogenetic time trees (Thesis, Doctor of Philosophy). University of Otago. Retrieved from \url{http://hdl.handle.net/10523/12606}}

\todo[inline]{Google Scholar thinks the arxiv version of this paper is a different paper -- should I add it here?}
\cvitem{}{\textbf{Collienne, L.}, Elmes, K., Fischer, M., Bryant, D. \& Gavryushkin, A. (2021). Discrete Coalescent Trees. \textit{Journal of Mathematical Biology 83.5, p. 60. issn: 1432-1416.}}

\cvitem{}{\textbf{Collienne, L.} \& Gavryushkin, A. (2021). Computing nearest neighbour interchange distances between ranked phylogenetic trees. \textit{Journal of Mathematical Biology 82.1, p. 8. issn: 1432-1416}.}

\cvitem{}{\textbf{Collienne, L.}, Elmes, K., Fischer, M., Bryant, D., \&
Gavryushkin, A. (2019). Geometry of Ranked Nearest Neighbour Interchange Space
of Phylogenetic Trees. \textit{BioRxiv}.}
%----------------------------------------------------------------------------------------



\end{document}